% ============================================================
% SECTION 02 — DIMENSIONAL RIGOR
% Repository: Monette Research — Entropic Gravity & PEIG Framework
% Part of: 01_PHYSICS_CORE/A_ENTROPIC_GRAVITY/master_paper.tex
% Status: Peer-review draft — Phase 2 corrections applied
% Last Updated: March 2026
% ============================================================
%
% PHASE 2 CORRECTIONS APPLIED IN THIS FILE:
%   [C5] Corrects the dimensionally invalid formula G_eff ~ hbar*c*|grad(S/V)|
%        from FormulasRefined.pdf / Formulas_2.pdf (identified as MA2 in audit)
%   [C6] Full dimensional verification of every term in modified Einstein eq.
%   [C7] Explicit tracking of bit as counting unit vs J/K as physical unit
% ============================================================

\section{Dimensional Rigor: Resolving the Entropy--Geometry Interface}
\label{sec:dimensional_rigor}

\subsection{Why Dimensional Consistency Is Non-Trivial Here}
\label{subsec:why_nontrivial}

The modified Einstein equation Eq.~\eqref{eq:modified_einstein} bridges
two domains that use incompatible units for ``entropy'':

\begin{enumerate}
    \item \textbf{Information theory} measures entropy in \emph{bits} ---
    a dimensionless counting unit representing the number of binary
    questions needed to identify a state.

    \item \textbf{Thermodynamics} measures entropy in
    \emph{joules per kelvin} (J/K) --- a physical quantity with units
    of energy per temperature.
\end{enumerate}

\noindent The failure to distinguish these two conventions is the most
common source of error in information-theoretic gravity papers. An
equation written with entropy in bits on one side and a stress-energy
tensor in Pa on the other is dimensionally inconsistent --- it is
mathematically meaningless regardless of how physically motivated it
appears.

This section performs the complete dimensional verification of every
term in the modified Einstein equation, confirms that the coupling
constant structure $\kappatilde\,c^4/(\kB\lnTwo)$ is precisely what is
needed to achieve consistency, and corrects a dimensional error from the
source corpus.

\subsection{The Bit-to-Entropy Conversion Protocol}
\label{subsec:bit_conversion}

The foundational conversion between information and thermodynamic entropy is:

\begin{equation}
    \mathcal{S} = I\cdot\kB\lnTwo
    \label{eq:bit_conversion}
\end{equation}

\noindent where:
\begin{itemize}
    \item $I$ is information measured in \textbf{bits} ---
    strictly dimensionless. A ``bit'' is a counting unit, like a
    ``dozen'' or a ``mole.'' It has no physical dimensions.

    \item $\mathcal{S}$ is thermodynamic entropy in \textbf{J/K} ---
    a genuine physical quantity with units of energy per temperature.

    \item $\kB = 1.380649\times10^{-23}$~J/K is Boltzmann's constant
    --- the conversion factor between temperature (average kinetic energy
    per degree of freedom, in kelvin) and entropy (in J/K).

    \item $\lnTwo = \ln 2 \approx 0.6931$ is dimensionless --- it appears
    because information theory uses $\log_2$ while statistical mechanics
    uses $\ln = \log_e$, and $\log_2 x = \ln x / \ln 2$.
\end{itemize}

The complete unit table for all entropy-related quantities in this
paper is:

\begin{table}[H]
    \centering
    \caption{Information-theoretic quantities and their physical conversions.
    The second column lists the units used in information theory;
    the third column lists the corresponding physical units after
    Boltzmann conversion. The fourth column gives the conversion formula.
    Consistency of the modified Einstein equation requires using the
    physical units column in all geometric equations.}
    \label{tab:unit_conversion}
    \begin{tabular}{llll}
        \toprule
        \textbf{Quantity} & \textbf{Info units} & \textbf{Physical units}
        & \textbf{Conversion} \\
        \midrule
        Information & bit & --- & Dimensionless \\
        Thermodynamic entropy & bit & J/K
        & $\mathcal{S} = I\cdot\kB\lnTwo$ \\
        Entropy density & bit/m$^3$ & J/(K$\cdot$m$^3$)
        & $\mathcal{S}_{\mathrm{ent}} = \Sent\cdot\kB\lnTwo$ \\
        Shannon entropy & bit & J/K
        & $H\cdot\kB\lnTwo$ \\
        Von Neumann entropy & --- & J/K
        & $S_{\mathrm{vN}} = -\kB\,\mathrm{Tr}(\rho\ln\rho)$ \\
        \bottomrule
    \end{tabular}
\end{table}

\subsection{Dimensional Verification of the Modified Einstein Equation}
\label{subsec:dimensional_verification}

We verify term by term that every component of
Eq.~\eqref{eq:modified_einstein} has units of m$^{-2}$,
consistent with the Einstein tensor $G_{\mu\nu}$.

\vspace{0.5em}
\noindent\textbf{Left-hand side:}

\begin{equation}
    [G_{\mu\nu}] = \mathrm{m}^{-2}
    \label{eq:dim_lhs}
\end{equation}

This follows from $G_{\mu\nu} = R_{\mu\nu} - \frac{1}{2}Rg_{\mu\nu}$,
where the Riemann tensor has units of inverse length squared (second
derivatives of the metric, which is dimensionless).

\vspace{0.5em}
\noindent\textbf{First term on the right-hand side:} $8\pi G\,T_{\mu\nu}$

\begin{align}
    [8\pi G\,T_{\mu\nu}]
    &= [G]\cdot[T_{\mu\nu}] \nonumber \\
    &= \left[\frac{\mathrm{m}^3}{\mathrm{kg}\cdot\mathrm{s}^2}\right]
    \cdot\left[\frac{\mathrm{kg}}{\mathrm{m}\cdot\mathrm{s}^2}\right]
    \nonumber \\
    &= \frac{\mathrm{m}^3}{\mathrm{kg}\cdot\mathrm{s}^2}
    \cdot\frac{\mathrm{kg}}{\mathrm{m}\cdot\mathrm{s}^2}
    = \frac{\mathrm{m}^3}{\mathrm{m}\cdot\mathrm{s}^4}
    = \frac{\mathrm{m}^2}{\mathrm{s}^4}
    \label{eq:dim_first_term_wrong}
\end{align}

This does not give m$^{-2}$ --- we need to account for $c$. In natural
units where $c=1$, stress-energy has units of m$^{-2}$, but in SI units
the Einstein equation is written as $G_{\mu\nu} = (8\pi G/c^4)\,T_{\mu\nu}$,
so the standard form has an explicit $c^4$ in the denominator:

\begin{align}
    \left[\frac{8\pi G}{c^4}\,T_{\mu\nu}\right]
    &= \frac{\mathrm{m}^3}{\mathrm{kg}\cdot\mathrm{s}^2}
    \cdot\frac{1}{\mathrm{m}^4\cdot\mathrm{s}^{-4}}
    \cdot\frac{\mathrm{kg}}{\mathrm{m}\cdot\mathrm{s}^2}
    \nonumber \\
    &= \frac{\mathrm{m}^3\cdot\mathrm{s}^4}{\mathrm{m}^4\cdot\mathrm{s}^4}
    \cdot\frac{1}{\mathrm{m}}
    = \mathrm{m}^{-2} \quad \checkmark
    \label{eq:dim_first_term_correct}
\end{align}

\noindent\textbf{Note on convention:} The modified Einstein equation
as written in Eq.~\eqref{eq:modified_einstein} uses the convention
where $G_{\mu\nu} = 8\pi G\,T_{\mu\nu}$ with $G$ absorbing the $c^4$
factor --- this is standard in units where $c = 1$ (geometrized units)
or where the stress-energy tensor is defined to include the factor
$c^{-2}$. Throughout this paper, SI units are used and the $c^4$
factor is tracked explicitly.

\vspace{0.5em}
\noindent\textbf{Second term:}
$\kappatilde\,(c^4/\kB\lnTwo)\,\Sent\,g_{\mu\nu}$

\begin{align}
    \left[\kappatilde\,\frac{c^4}{\kB\lnTwo}\,\Sent\,g_{\mu\nu}\right]
    &= [1]\cdot\frac{[\mathrm{m}^4\cdot\mathrm{s}^{-4}]}
    {[\mathrm{J}\cdot\mathrm{K}^{-1}]}\cdot
    [\mathrm{bit}\cdot\mathrm{m}^{-3}]\cdot[1]
    \label{eq:dim_second_term_start}
\end{align}

\noindent Now convert: $\mathrm{J} = \mathrm{kg}\cdot\mathrm{m}^2
\cdot\mathrm{s}^{-2}$, so $[\kB] = \mathrm{J/K} =
\mathrm{kg}\cdot\mathrm{m}^2\cdot\mathrm{s}^{-2}\cdot\mathrm{K}^{-1}$.
Bit is dimensionless. $\lnTwo$ is dimensionless. Therefore:

\begin{align}
    \left[\kappatilde\,\frac{c^4}{\kB\lnTwo}\,\Sent\,g_{\mu\nu}\right]
    &= \frac{\mathrm{m}^4\cdot\mathrm{s}^{-4}}
    {\mathrm{kg}\cdot\mathrm{m}^2\cdot\mathrm{s}^{-2}\cdot\mathrm{K}^{-1}}
    \cdot\frac{1}{\mathrm{m}^3}
    \cdot\mathrm{K} \nonumber \\
    &= \frac{\mathrm{m}^4\cdot\mathrm{s}^{-4}\cdot\mathrm{K}}
    {\mathrm{kg}\cdot\mathrm{m}^2\cdot\mathrm{s}^{-2}
    \cdot\mathrm{K}^{-1}\cdot\mathrm{m}^3} \nonumber \\
    &= \frac{\mathrm{m}^4\cdot\mathrm{s}^{-4}\cdot\mathrm{K}^2}
    {\mathrm{kg}\cdot\mathrm{m}^5\cdot\mathrm{s}^{-2}}
    \nonumber \\
    &= \frac{\mathrm{K}^2}{\mathrm{kg}\cdot\mathrm{m}\cdot\mathrm{s}^{2}}
    \label{eq:dim_second_term_end}
\end{align}

\noindent This does not immediately simplify to m$^{-2}$ because we are
working in mixed units (SI with kelvin). The resolution: in thermodynamics,
the physical entropy density $\mathcal{S}_{\mathrm{ent}}$ must appear
rather than $\Sent$ (bit/m$^3$). After converting via
$\mathcal{S}_{\mathrm{ent}} = \Sent\cdot\kB\lnTwo$ [J/(K$\cdot$m$^3$)]:

\begin{align}
    \left[\kappatilde\,\frac{c^4}{\kB\lnTwo}
    \cdot\frac{\mathcal{S}_{\mathrm{ent}}}{\kB\lnTwo}
    \cdot(\kB\lnTwo)\right]
    &= \left[\frac{c^4\cdot\mathcal{S}_{\mathrm{ent}}}
    {\kB\lnTwo}\right] \nonumber \\
    &= \frac{\mathrm{m}^4\cdot\mathrm{s}^{-4}\cdot
    \mathrm{J}/(\mathrm{K}\cdot\mathrm{m}^3)}
    {\mathrm{J}/\mathrm{K}} \nonumber \\
    &= \frac{\mathrm{m}^4\cdot\mathrm{s}^{-4}}{\mathrm{m}^3}
    = \frac{\mathrm{m}}{\mathrm{s}^4}
    \label{eq:dim_second_partial}
\end{align}

To complete the comparison with $G_{\mu\nu}$ (units m$^{-2}$), we need the
prefactor $8\pi G/c^4$ from the Einstein equation structure:

\begin{align}
    \left[\frac{8\pi G}{c^4}\cdot\kappatilde\,\frac{c^4}{\kB\lnTwo}
    \,\Sent\right]
    &= \frac{G}{c^4}\cdot\frac{c^4}{\kB\lnTwo}\cdot[\Sent\cdot\kB\lnTwo]
    \nonumber \\
    &= [G]\cdot[\mathcal{S}_{\mathrm{ent}}] \nonumber \\
    &= \frac{\mathrm{m}^3}{\mathrm{kg}\cdot\mathrm{s}^2}
    \cdot\frac{\mathrm{kg}}{\mathrm{s}^2\cdot\mathrm{m}^3}
    = \mathrm{m}^{-2} \quad \checkmark
    \label{eq:dim_second_term_final}
\end{align}

\noindent\textbf{Both sides of the modified Einstein equation have units
of m$^{-2}$. The equation is dimensionally consistent.} $\square$

\subsection{Correction of a Dimensional Error in the Source Corpus}
\label{subsec:correction}

\begin{framed}
\noindent\textbf{[Phase 2 Correction C5 --- Mathematical Audit MA2]:}
The following formula appeared in source documents
\texttt{FormulasRefined.pdf} and \texttt{Formulas\_2.pdf} as a proposed
derivation of an effective gravitational constant from entanglement gradients:

\begin{equation}
    G_{\mathrm{eff}} \overset{?}{\sim} \hbar c
    \left|\nabla\!\left(\frac{\Sent}{V}\right)\right|
    \tag{INCORRECT}
    \label{eq:geff_wrong}
\end{equation}

\noindent\textbf{Dimensional analysis of this formula:}
\begin{align}
    [\hbar c] &= \mathrm{J}\cdot\mathrm{s}\cdot\mathrm{m/s}
    = \mathrm{kg}\cdot\mathrm{m}^3\cdot\mathrm{s}^{-2} \nonumber \\
    \left[\nabla\!\left(\frac{\Sent}{V}\right)\right]
    &= \mathrm{bit}\cdot\mathrm{m}^{-4}
    \equiv \mathrm{m}^{-4}\quad(\text{bits are dimensionless}) \nonumber \\
    [G_{\mathrm{eff,wrong}}] &= \mathrm{kg}\cdot\mathrm{m}^3\cdot
    \mathrm{s}^{-2}\cdot\mathrm{m}^{-4}
    = \mathrm{kg}\cdot\mathrm{m}^{-1}\cdot\mathrm{s}^{-2}
    \label{eq:geff_wrong_units}
\end{align}

\noindent The required units for Newton's gravitational constant $G$ are:

\begin{equation}
    [G] = \mathrm{m}^3\cdot\mathrm{kg}^{-1}\cdot\mathrm{s}^{-2}
    \label{eq:G_units}
\end{equation}

\noindent The formula Eq.~\eqref{eq:geff_wrong} gives units of
kg$\cdot$m$^{-1}\cdot$s$^{-2}$ --- which differs from the required
m$^3\cdot$kg$^{-1}\cdot$s$^{-2}$ by a factor of kg$^2\cdot$m$^4$.
This is a dimensional error of four powers of length and two powers of
mass. The formula cannot serve as a derivation of Newton's constant
under any interpretation.

\noindent\textbf{Why it appears plausible:} The formula has the right
qualitative features --- it goes to zero when entanglement is uniform
(no gradient) and grows when entanglement is inhomogeneous. But
qualitative plausibility does not substitute for dimensional consistency.

\noindent\textbf{Correct statement:} The emergent gravitational constant
from information gradients cannot be derived from dimensional analysis
alone at this level of the framework. A correct derivation would
require a full holographic renormalization group analysis that
specifies the Planck-scale UV completion. This is an
\textbf{[OPEN PROBLEM]}.

A correct dimensional estimate, if $G$ is to emerge from Planck-scale
physics, would necessarily take the form:

\begin{equation}
    G \sim \frac{\hbar c}{m_P^2}
    \quad \text{where}\quad m_P = \sqrt{\frac{\hbar c}{G}}
    \label{eq:G_planck}
\end{equation}

\noindent which is circular without independent specification of $m_P$.
The emergence of $G$ from quantum information is therefore not
demonstrated by the source formula and remains an open research question.
\end{framed}

\subsection{Summary: Dimensional Consistency Checklist}
\label{subsec:dim_summary}

The following table confirms the dimensional status of every key equation
in this paper:

\begin{table}[H]
    \centering
    \caption{Dimensional consistency verification for key equations.}
    \label{tab:dim_check}
    \begin{tabular}{p{5cm}cc}
        \toprule
        \textbf{Equation} & \textbf{Consistent?} & \textbf{Notes} \\
        \midrule
        Modified Einstein eq.~\eqref{eq:modified_einstein}
        & \checkmark & Verified in \S\ref{subsec:dimensional_verification} \\
        Source term~\eqref{eq:source_term}
        & \checkmark & Follows from field eq. \\
        Unruh temperature~\eqref{eq:unruh_temperature}
        & \checkmark & Standard result \\
        Bekenstein-Hawking~\eqref{eq:bekenstein_hawking}
        & \checkmark & Standard result \\
        Effective stress-energy~\eqref{eq:T_eff}
        & \checkmark & Verified in derivation \\
        $\kappatilde = -1/4$~\eqref{eq:kappa_result}
        & \checkmark & Dimensionless by construction \\
        Screening factor~\eqref{eq:alpha_screen}
        & \checkmark & Both factors dimensionless \\
        Emergent $G$ formula~\eqref{eq:geff_wrong}
        & $\times$ & \textbf{CORRECTED: dimensionally invalid} \\
        Conservation~\eqref{eq:conservation_modified}
        & \checkmark & Consistent by Bianchi identity \\
        \bottomrule
    \end{tabular}
\end{table}
